\documentclass[11pt]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage{setspace}
\usepackage{csquotes}
\title{}
\author{}
\date{}
\doublespacing
\usepackage{fancybox}


\begin{document}
\begin{flushright}
Aarush Chaubey\\
Per. 7\\
Ted Talk\\
\end{flushright}
\doublebox{
\parbox{\textwidth}{
      Prompt: \textit{Can we remedy or remediate human evil or human suffering?
}
       }
       
}

\vspace{5mm}

As seen by the recent elementary school shooting in Uvalde, Texas and all the other countless acts of mass violence in America preceding this one, there probably won’t be an end to human evil, and, as a result, there probably won’t be an end to human suffering as well. However, this doesn’t mean we can’t reduce the magnitude of the suffering caused by evil. Let’s take mass shootings for an example of evil. There have been several proposed solutions, such as implementing nationwide increased background checks to ensure a person who is unfit to wield a firearm doesn’t have access to one, buyback programs where the federal government pays individuals who give away their guns, and even arming more people with firearms to provide for a quicker response to a shooter. While the effectiveness of these solutions may be questioned, it doesn’t matter how valid the proposals are if government officials are unwilling to pass them. The fact of the matter is that we’ve been trying to pass gun legislation since the Columbine shooting more than 20 years ago, but those efforts have clearly amounted to nothing since we continue to face these issues. Now, this might seem as more of a rant than a concentrated paper; however, it’s important to emphasize the lack of progress from the United States government in order to realize that our attempts at remedying human evil and suffering could easily be futile. That is, if one of the most socioeconomically powerful countries in the world can’t remedy human suffering, can anybody? As a country, we promised ourselves to make sure the atrocities of the Columbine shooting didn’t happen again. We then promised the same after the Sandy Hook shooting, the same after the 2017 Las Vegas shooting, the same after the Parkland shooting, and now the same for the Uvalde shooting. It’s time to realize that human atrocities will never waver in strength or frequency, and as more people are killed every day, it’s also time to realize that we’ve broken our promise to ourselves and our country. 
\end{document}
